### 2016-02-13 Manuscript/BiologyLetters/Supplementary/ESM_1.tex
Dealt with comments

were \textit{order} was replaced by all the keywords listed above. For each 33 keywords, we selected the 20 first papers to match the Google search published since 2010 resulting in 660 papers.
Among these papers, not all contained relevant data (discrete morphological characters AND mammalian data).
We selected only the 20 first results per search term to avoid downloading articles that were too irrelevant.
Among the 660 papers, only 50 contained a total of 425 extra living OTUs (Figure ~\ref{Supp_figure_google_searches}).
Also we decided to select only the articles published since 2010 because nearly every one of the recent published matrix contains both a fraction of morphological characters and OTUs from previous studies.
For example in primates the character \textit{p7} coded first by \cite{ross1998phylogenetic} is reused with the same living species in \cite{seiffert2003fossil}, \cite{marivaux2005anthropoid}, \cite{seiffert2005basal}, \cite{bloch2007new}, \cite{bloch2007new}, \cite{kay2008anatomy}, \cite{silcox2008biogeographic}, \cite{seiffert2009convergent}, \cite{tabuce2009anthropoid}, \cite{boyer2010astragalar}, \cite{seiffert2010fossil}, \cite{marivaux2013djebelemur} and \cite{ni2013oldest}.

For example, the six living primates used in \cite{ross1998phylogenetic} (\textit{Aotus trivirgatus, Galago demidoff, Lemur catta, Microcebus murinus, Nycticebus coucang and Saimiri sciureus}) and their associated characters are reused along with more living species and characters in \cite{seiffert2003fossil}, \cite{marivaux2005anthropoid}, \cite{seiffert2005basal}, \cite{bloch2007new}, \cite{bloch2007new}, \cite{kay2008anatomy}, \cite{silcox2008biogeographic}, \cite{seiffert2009convergent}, \cite{tabuce2009anthropoid}, \cite{boyer2010astragalar}, \cite{seiffert2010fossil}, \cite{marivaux2013djebelemur} and \cite{ni2013oldest}.

>>>>

were \textit{order} was replaced by all the keywords listed above. For each 33 keywords, we selected the 20 first papers to match the Google search published since 2010 resulting in 660 papers.
Among these papers, not all contained relevant data (discrete morphological characters AND mammalian data).
We selected only the 20 first results per search term to avoid downloading articles that were too irrelevant.
Among the 660 papers, only 50 contained a total of 425 extra living OTUs on a total of 4950 OTUs (Figure ~\ref{Supp_figure_google_searches}).
Also we decided to select only the articles published since 2010 because nearly every one of the recent published matrix contains both a fraction of morphological characters and OTUs from previous studies.
For example, the six living primates used in \cite{ross1998phylogenetic} (\textit{Aotus trivirgatus, Galago demidoff, Lemur catta, Microcebus murinus, Nycticebus coucang and Saimiri sciureus}) and their associated characters are reused along with more living species and characters in \cite{seiffert2003fossil}, \cite{marivaux2005anthropoid}, \cite{seiffert2005basal}, \cite{bloch2007new}, \cite{bloch2007new}, \cite{kay2008anatomy}, \cite{silcox2008biogeographic}, \cite{seiffert2009convergent}, \cite{tabuce2009anthropoid}, \cite{boyer2010astragalar}, \cite{seiffert2010fossil}, \cite{marivaux2013djebelemur} and \cite{ni2013oldest}.

### 2016-02-13 Manuscript/BiologyLetters/Table_results.tex
Dealt with comments

% latex table generated in R 3.2.3 by xtable 1.8-0 package
% Mon Feb  8 22:09:15 2016
\begin{longtable}{lL{1.8cm}C{2cm}lcc}
\caption{Number of taxa with available cladistic data for mammalian orders at three
taxonomic levels. The left vertical bar represents low coverage (<25\%; coloured in blue); the right vertical bar represents high coverage (>75\%; coloured in orange). Negative Net Relatedness Index (NRI) and Nearest Taxon Index (NTI) values indicate phylogenetic overdispersion; positive values indicate phylogenetic clustering. Significant NRI or NTI values are in bold. *p <0.05; **p <0.01; ***p <0.001.
} \\ 

>>>>

% latex table generated in R 3.2.3 by xtable 1.8-0 package
% Mon Feb  8 22:09:15 2016
\begin{longtable}{lL{1.8cm}C{2cm}lcc}
\caption{Number of taxa with available cladistic data for mammalian orders at three
taxonomic levels. The left vertical bar represents low coverage (\textless 25\%; coloured in blue); the right vertical bar represents high coverage (\textgreater 75\%; coloured in orange). Negative Net Relatedness Index (NRI) and Nearest Taxon Index (NTI) values indicate phylogenetic overdispersion; positive values indicate phylogenetic clustering. Significant NRI or NTI values are in bold. *p \textless 0.05; **p \textless 0.01; ***p \textless 0.001.
} \\
